Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-24 paper.tex
a few small edits to the intro

Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews that users use when selecting products, restaurants, and vacation destinations.  Users of these websites wish to choose the product / restaurant / vacation (item) that is best according to their preference over attributes, and rely on previous users' reviews to estimate these attributes.  These reviews provide not just cardinal feedback, but also a description of attributes that a user with different preferences may use to select their preferred item.  An item with only a small number of reviews might have inaccurate attribute estimates, leading users to choose not to try it even though it may actually be the best choice for some subset of those users.  Without incentives, this situation may persist and decrease welfare for the platform's user base.  By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.

We can also apply our models to scientific organizations like eBird \cite{frazier2014incentivizing}. EBird is a website which guides the enthusiasts to explore and report their findings to the bird community. In each report, it contains information such as when, where and how they go birding as well as what kinds of birds they see and hear. As the orginization, EBird needs to incentivize the enthusiasts to explore the less-explored parts of domain. For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc. By offering enthusiasts incentivies, eBirds can obtain more reports about the less-explored area and have more information for the bird community.\bccomment{How about this eBird application?}

@@

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold. In our paper, we assume all arms are some agents' best arm. Under this assumption, we prove with $O(N^2)$ payment budget, we can bound the cumulative expected regret by $O(N^2+M(\log(T))^2)$ where $M$ is the upper bound of the marginal density for those agents who are indifferent between their best and the second best arm. In the case that $M=0$, which typically happens when the user preference distribution is discrete, we can achieve constant cumulative expected regret $O(N^2)$. The key difference between our problem setting and the homogenous preference setting (or the traditional multi-armed bandits setting) is that we do not need to incentivize the agents to try a suboptimal arm very often since all arms are some agents's best arm. These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings. Essentially, heterogeneity provides a certain amount of exploration for free. \bccomment{How about now?}

We broadly categorize the literature into two categories based on whether there is money transfer.
With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore. In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget. \cite{han2015incentivizing} generalizes this framework to allow agents have heterogeneous value of money. Further, it assumes there is a external signal scheme which provides partial information about each agent. Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.

Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time. \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time. \cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other. In these papers, the principal provides each agent an recommendation at each time, which is Bayesian incentive-compatible. They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.

We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is at least $\Omega(\log(T))$ in the worst case, regardless of incentive budget.

>>>>

Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.  Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.  These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.  An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.  Without incentives, this situation may persist and decrease welfare for the platform's user base.  By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.

Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing}. \pfcomment{Can you also cite their website?} EBird guides birding enthusiasts through a website to explore and report their findings to the birding community. Each user report contains information about when, where and how they go birding and what birds they see and hear. EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations. Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety. By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.

@@

In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold. In our paper, we assume all arms are some agents' best arm. Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm. If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$. The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.  Essentially, heterogeneity provides free exploration.  These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.

We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore. This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget. \cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation. Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.

Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time. \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time. \cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other. In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible. They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.

We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget \pfcomment{This should be $N^2$, right?  Also, do you want to add $M$ in here?}; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
